Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-11 paper.qmd
Added colors to images

```{r}
#| label: plot-theme
theme_set(theme_linedraw() +
   theme(
     #aspect.ratio = 1,
     plot.background = element_rect(fill = 'transparent', colour = NA),
     plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
     panel.background = element_rect(fill = 'transparent', 
                                     colour = NA),
     panel.grid.major = element_blank(), 
     panel.grid.minor = element_blank(), 
     axis.title.x = element_blank(), axis.title.y = element_blank(),
     axis.text.x = element_blank(), axis.ticks.x = element_blank(),
     axis.text.y = element_blank(), axis.ticks.y = element_blank(),
     legend.background = element_rect(fill = 'transparent', 
                                      colour = NA),
     legend.key = element_rect(fill = 'transparent', 
                               colour = NA),
     legend.position = "bottom", 
     legend.title = element_blank(), 
     legend.text = element_text(size=4),
     legend.key.height = unit(0.25, 'cm'),
     legend.key.width = unit(0.25, 'cm')
   )
)
interior_annotation <- function(label, position = c(0.92, 0.92), cex = 1) {
  annotation_custom(grid::textGrob(label = label,
      x = unit(position[1], "npc"), y = unit(position[2], "npc"),
      gp = grid::gpar(cex = cex, col="grey70")))
}
```

@@

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "Light Grays")
  # scale_colour_brewer(
  #   type = "seq",
  #   palette = 1
  # ) #+ 
  # theme(
  #     legend.position = "bottom",
  #     legend.text = element_text(size = 10),          # Increase legend text size
  #     legend.key.size = unit(1, "lines")              # Increase size of legend keys
  # ) +
  # guides(
  #     color = guide_legend(
  #         override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
  #     )
  # ) 
```

@@

right_top_img <- pixels_gathered_within |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")

@@

middle_img <- pixels_gathered_within |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")

@@

right_bottom_img <- pixels_gathered_within |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")

@@

imge_error_sample_outside <- pixels_gathered_outside |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")

>>>>

```{r}
#| label: plot-theme
theme_set(theme_linedraw() +
   theme(
     #aspect.ratio = 1,
     plot.background = element_rect(fill = 'transparent', colour = NA),
     plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
     panel.background = element_rect(fill = 'transparent', 
                                     colour = NA),
     panel.grid.major = element_blank(), 
     panel.grid.minor = element_blank(), 
     axis.title.x = element_blank(), axis.title.y = element_blank(),
     axis.text.x = element_blank(), axis.ticks.x = element_blank(),
     axis.text.y = element_blank(), axis.ticks.y = element_blank(),
     legend.background = element_rect(fill = 'transparent', 
                                      colour = NA),
     legend.key = element_rect(fill = 'transparent', 
                               colour = NA),
     legend.position = "bottom", 
     legend.title = element_blank(), 
     legend.text = element_text(size=4),
     legend.key.height = unit(0.25, 'cm'),
     legend.key.width = unit(0.25, 'cm')
   )
)
interior_annotation <- function(label, position = c(0.92, 0.92), cex = 1, col="grey70") {
  annotation_custom(grid::textGrob(label = label,
      x = unit(position[1], "npc"), y = unit(position[2], "npc"),
      gp = grid::gpar(cex = cex, col=col)))
}
```

@@

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "Light Grays") +
  geom_rect(aes(xmin = 0.8, xmax = 0.9, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#e41a1c", linewidth = 0.7) +
  geom_rect(aes(xmin = 0.4, xmax = 0.5, ymin = 0.75, ymax = 0.9),
               fill = "transparent", color = "#377eb8", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.45, xmax = 0.55, ymin = 0.75, ymax = 0.9),
               fill = "transparent", color = "#4daf4a", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.55, xmax = 0.65, ymin = 0.75, ymax = 0.9),
               fill = "transparent", color = "#984ea3", linewidth = 0.7) 
  # scale_colour_brewer(
  #   type = "seq",
  #   palette = 1
  # ) #+ 
  # theme(
  #     legend.position = "bottom",
  #     legend.text = element_text(size = 10),          # Increase legend text size
  #     legend.key.size = unit(1, "lines")              # Increase size of legend keys
  # ) +
  # guides(
  #     color = guide_legend(
  #         override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
  #     )
  # ) 
```

@@

right_top_img <- pixels_gathered_within |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Blues 3") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")

@@

middle_img <- pixels_gathered_within |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Greens 3") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")

@@

right_bottom_img <- pixels_gathered_within |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Purples 2") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")

@@

imge_error_sample_outside <- pixels_gathered_outside |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Reds 2") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")
